Isomorphisms between algebraic datatypes

### 2024-12-16 QADT/notes.tex
QADT clean-up phase 1
QADT notes

\newcommand{\ints}{\mathbb{Z}}

@@

>>>>

\newcommand{\ints}{\mathbb{Z}}
\newcommand{\nat}{\mathbb{N}}

@@

\section{Standard ADTs}
\begin{itemize}
  \item $s(X) = 1 + 2\cdot X$, $S = \mu X. s(x)$
  \item $t(X) = 1 + X^2$, $T = \mu X. t(x)$
  \item $m(X) = 1 + X + X^2$, $M = \mu X. m(x)$
  \item $j(X) = 1 + 2X + X^2$, $J = \mu X. j(x)$
  \item $h(X) = 1 + X + X^3$, $H = \mu X. h(x)$
  \item $h(X) = 1 + X^2 + X^4$
\end{itemize}

\section{Research problems}
\subsection{Relating different ``roots'' of a single ADT}

Enumerate/define the polynomials that leave the given ADT unchanged

Examples:
\begin{enumerate}
  \item $T = T^5$
  \item $M = M^3$
  \item $J = J^2$
\end{enumerate}

\subsection{Relating different ADTs in terms of their roots}
\begin{enumerate}
  \item $T^3 = M^2$
  \item $T^3$ and $M^2$ vs. $S$?
  \item
\end{enumerate}

\subsection{A type theory defining equality without triple equality}

\section{Definitions}

\begin{itemize}
  \item Let $\nat[x]$ be the set of all polynomials in variable $x$ with coefficients in $\nat$
  \item This is the free rig over ${x}$
  \item Consider the left action of $\nat[x]$ on itself: $\_\cdot\_ : \nat[x] \times \nat[x] \to \nat[x]$ and $(p(x) , q(x)) \mapsto p(x) \cdot q(x)$
  \item If we now consider the quotient $\nat[x] / ((1) x=2x+1 , (2) x+x^2=1+x)$, we find that the induced action satisfies \[(x\cdot) \circ (x\cdot) = id\]
  \item With (2), every $p(x)$ is equivalent to $a+bx$
  \item With (1), every $a+b\cdot x$ is equivalent to one of: \[\begin{cases}
    a & a \ge 0 \\
    a + x & a                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \ge 0 \\
    bx & b \ge 1
  \end{cases}\]
\end{itemize}

\section{2024.08.23}

\begin{itemize}
  \item Can we define LFP in a way that is positive?
\end{itemize}
